New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-02-17 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
plots fitbit

  plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth() +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold")) + 
    theme_apa() 
    # facet_grid(cols = vars(time_span),
    #          scales = "free_x")

>>>>

  loess_plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 1,
              colour = "red") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
  scale_y_continuous(breaks = seq(0, 160, 5)) + 
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  ggtitle("Gesamtverlauf Herzrate in unterschiedlichen Phasen") +
  theme_apa() + 
  theme(text = element_text(family = "sans"),
        legend.text = element_text(size = 20),
        legend.title = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        strip.text = element_text(size = 15),
        plot.title = element_text(size = 20, 
                                  face = "bold"))
loess_plot_overall

# saving plot 
ggsave(plot = loess_plot_overall,
       filename = "plots/loess_plot_overall.svg",
       height = 5,
       width = 8,
       units = "in")

## Plot mit Mittelwerten und SDs

# checking for outliers
# df_outliers <-
#   main %>% 
#   filter(time_span != "overall") %>%   
#   dplyr::select("ID",
#          "time_span",
#          "heart_rate",
#          "teaching_experience",
#          "disruption_factor",
#          "confidence_factor") %>% 
#   mutate(time_span = fct_recode(time_span,
#                                 "Pre-Lehrphase" = "pre",
#                                 "Lehrphase" = "main",
#                                 "Post-Lehrphase" = "subsequent",
#                                 "Interviewphase" = "interview",
#                                 "Endphase" = "after"
#                                 ),
#          time_span = factor(time_span,
#                             levels = c("Pre-Lehrphase",
#                                        "Lehrphase",
#                                        "Post-Lehrphase",
#                                        "Interviewphase",
#                                        "Endphase"
#                                        )
#                             )
#          ) %>%
#   distinct() %>% 
#   group_by(ID, time_span) %>%
#   summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
#             sd_hr = sd(heart_rate, na.rm = TRUE)
#             ) %>% 
#   group_by(time_span) %>%
#   identify_outliers(mean_hr)
# 
# # exclude extreme outliers
# df_plot_mean <-
#   df_outliers %>% 
#   filter(!mean_hr %in% c("131.7869",
#                          "129.3250",
#                          "137.8485",
#                          "136.9259",
#                          "109.2143",
#                          "110.6800",
#                          "107.0800"))

# data wrangling - preparing data for plotting
df_plot_mean <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("time_span",
                "heart_rate") %>% 
  mutate(time_span = fct_recode(time_span,
                                "(1) Pre-Lehrphase" = "pre",
                                "(2) Lehrphase" = "main",
                                "(3) Post-Lehrphase" = "subsequent",
                                "(4) Interviewphase" = "interview",
                                "(5) Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("(1) Pre-Lehrphase",
                                       "(2) Lehrphase",
                                       "(3) Post-Lehrphase",
                                       "(4) Interviewphase",
                                       "(5) Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(time_span) %>%
  summarise_at(vars(heart_rate),
               list(mean_hr = mean,
                    sd_hr = sd)
               ) %>% 
  as.data.frame()

# plotting
plot_mean_sd <- 
  ggplot(df_plot_mean, 
         aes(x = time_span, y = mean_hr)) + 
  geom_point(size = 5,
             colour = "red")+
  geom_errorbar(aes(ymin = mean_hr - sd_hr, 
                    ymax = mean_hr + sd_hr), 
                width=.2,
                position = position_dodge(0.05)) + 
  scale_y_continuous(breaks = seq(0, 160, 10)) +
  labs(x = "",
       y = "Herzrate (in Schlägen pro Minute)") +
  ggtitle("Herzrate (M, SD) in unterschiedlichen Phasen") +
  theme_apa() + 
  theme(text = element_text(family = "sans"),
        legend.text = element_text(size = 20),
        legend.title = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        axis.text.x = element_text(size = 11, colour = "black"),
        axis.text.y = element_text(size = 11),
        strip.text = element_text(size = 15),
        plot.title = element_text(size = 20, 
                                  face = "bold"))
plot_mean_sd

# saving plot 
ggsave(plot = plot_mean_sd,
       filename = "plots/plot_mean_sd.svg",
       height = 5,
       width = 8,
       units = "in")

### 2023-02-17 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
plots fitbit

The sample consisted in total of \emph{N} = 63 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 61 subjects.

The subjects (39 women; 63.93 \%) had a mean age of 29.60 years (\emph{SD} = 10.40; range: 19-59) and an average teaching experience of 4.66 years (\emph{SD} = 9.30; range: 0-37).

18.03\% of the subjects were (studying to become) teachers for primary school, 72.13\% were (studying to become) teachers for secondary school and 9.84\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 96.26 bpm with a standard deviation of 14.22 and a range from 56 to 139 bpm.

@@

>>>>

The sample consisted in total of \emph{N} = 72 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.

The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).

17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-psych}{}}%
Revelle, W. (2022). \emph{Psych: Procedures for psychological, psychometric, and personality research}. Evanston, Illinois: Northwestern University. Retrieved from \url{https://CRAN.R-project.org/package=psych}
